---
title: "Shiny Application and Reproducible Pitch"
output: ioslides_presentation
date: '2022-07-03'
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo=FALSE, include=FALSE}
#Load libraries
library('ggplot2')
library('tidyverse')
library('datasets')
library('dplyr')
library('shiny')
library('rsconnect')

```


## Overview

This assignment is related to Developing Data Products course.

It used data from 'mtcars',a data set of cars collection from Motor Trend, and run regression models to explore the relation between a set of variables and miles per gallon (MPG).


## Data summary

Data set consists of 32 observations and 11 variables

```{r}
# Data preparation ----
mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))
summary(mpgData)
```

## About the app
It is a simple application where you can choose some variables from 'mtcars' data set including:

- Number of cylinders (cyl)
- Horsepower (hp)
- Weight (wt)
- Transmission (am)

and observe how they influence miles per gallon (MPG).

## Interactive model

```{r}
# UI Definition ----
ui <- fluidPage(
  titlePanel("The relationship between variables and (MPG)"),
  sidebarLayout(
    sidebarPanel(
      selectInput("variable", "Select variables:",
                  c("Number of cylinders" = "cyl","Horsepower" = "hp",
                    "Weight (lb/1000)" = "wt","Transmission" = "am")),
      checkboxInput("outliers", "Show BoxPlot's outliers", FALSE)), 
    mainPanel(h3(textOutput("caption")),
              tabsetPanel(type = "tabs",
                          tabPanel("BoxPlot", plotOutput("mpgBoxPlot")),
                          tabPanel("mpgSPlot", plotOutput("mpgSPlot")),
                          tabPanel("Regression model",plotOutput("mpgPlot"),
                                   verbatimTextOutput("fit"))))))
```


```{r}
# Define server logic ----
server <- function(input, output) {
  
  formulaText <- reactive({
    paste("mpg ~", input$variable)
  })
  
  formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")
  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mpgData)
  })
  
  output$caption <- renderText({
    formulaText()
  })
  
  output$mpgBoxPlot <- renderPlot({
    boxplot(as.formula(formulaText()), 
            data = mpgData,
            outline = input$outliers)
  })
  
  output$mpgSPlot <- renderPlot({
    ggplot(mpgData, aes_string(y=input$variable, x="mpg")) + geom_point()
  })
  
  output$fit <- renderPrint({
    summary(fit())
  })
  
  output$mpgPlot <- renderPlot({
    with(mpgData, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })
  })
  
}
```


```{r}
# Run the app ----
shinyApp(ui = ui, server = server)
```

## GitHub repository

Check the following link for code of application:

https://github.com/NazaninFarzady/Shiny-Application-and-Reproducible-Pitch

